Maintenance planning on French military aircraft operations

### 2018-08-22 R/presentations/CLAIO_presentation/presentation.Rmd
updated presentation for CLAIO

---
title: "Maintenance planning on French military aircraft operations"
author: |
    | Franco Peschiera, Alain Haït, Olga Battaïa, Nicolas Dupin
institute: "ISAE SUPAERO"
date: "September 24, 2018"
output: 
  beamer_presentation:
    theme: "Berlin"
    toc: true
    slide_level: 2
    incremental: yes
    fig_height: 4
    # footer: "ISAE-SUPAERO, Université de Toulouse, France"
    includes:
        in_header: header.tex
  slidy_presentation:
    css: ./../../css/baobab_MH.css
    incremental: yes
    footer: "ISAE-SUPAERO, Université de Toulouse, France"
    slide_level: 2
    toc: true
nocite: '@*'
bibliography: MFMP_NRP.bib
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
path_to_R_dir <- "./../../"
setwd(path_to_R_dir)
source('functions/params.R')
source('functions/import_results.R')
exp_directory = PATHS[['experiments']] %>% paste0('201802141539/')
gantt <- print_solution(exp_directory, max_resources = 30)
show_gantt <- knitr::opts_knit$get("rmarkdown.pandoc.to")=="slidy"
```

@@

if (show_gantt){
    htmltools::HTML('<div style="font-size: 20px;width:100%">')
    gantt
    htmltools::HTML("</div>")
} else {
    knitr::include_graphics('../img/calendar.png' %>% paste0(path_to_R_dir, .))
}

@@

## Complexity analysis

Similar to the 'Fixed interval scheduling' problem.

@@

<!-- TODO: make a design. -->

@@

<!-- ## Model: sets -->

<!-- |Set|Description| -->
<!-- |-----|--------------------------------------------------------------------| -->
<!-- |    $\mathcal{I}$       |  resources. | -->
<!-- |    $\mathcal{T}$       |  time periods inside planning horizon. | -->
<!-- |    $\mathcal{J}$       |  tasks. | -->
<!-- |    $\mathcal{T}_j$     |  time periods $t \in \mathcal{T}$ in which task $j$ is active. | -->
<!-- |    $\mathcal{J}_t$    |  tasks $j \in \mathcal{J}$ to be realized in period $t$. | -->
<!-- |    $\mathcal{I}_j$     |  resources $i \in \mathcal{I}$ that can be assigned to task $j$. | -->
<!-- |    $\mathcal{O}_i$     |  tasks $j \in \mathcal{J}$ for which resource $i$ can be used. | -->
<!-- |    $\mathcal{T}^{s}_t$ |  time periods $t' \in \mathcal{T}$ such that $t' \in \{ \max{\{1, t - M+1\}},  ..., {t}$\}. | -->

<!-- ## Model: main parameters -->

<!-- |Parameters|Description| -->
<!-- |--------------|-------------------------------------------------| -->
<!-- | $H_j$ |  amount of **resource time required** by task $j$. | -->
<!-- | $R_j$ |  number of **resources required** by task $j$. | -->
<!-- | $M$   |  **maintenance duration** in number of periods. | -->
<!-- | $E$   |  remaining **elapsed time** after a maintenance. | -->
<!-- | $H$   |  remaining **usage time** after a maintenance. | -->

<!-- ## Model: more parameters -->

<!-- |Parameters|Description| -->
<!-- |--------------|----------------------------------------------------------------------| -->
<!-- | $N_t$              | number of resources in already-planned maintenances in period $t$ at the beginning | of the planning ho |izon.| -->
<!-- | $D_t$              | number of resources to be assigned in total in period $t$. | -->
<!-- | $Rut^{Init}_{i}$   | remaining usage time for resource $i$ at the start of the planning horizon. | -->
<!-- | $Ret^{Init}_{i}$   | remaining elapsed time for resource $i$ at the start of the planning horizon. | -->
<!-- | $Ret^{Init}_{sum}$ | sum of remaining elapsed times at the start of the planning horizon. | -->
<!-- | $Rut^{Init}_{sum}$ | sum of remaining elapsed time at the start of the planning horizon. | -->

<!-- ## Model: variables -->

<!-- | Variable   |  Description | -->
<!-- |-----------|------------------------------------------------------- | -->
<!-- | $a_{jti}$   |  =1 if **task** $j \in J$ in period $t \in \mathcal{T}_j$ **is realized with resource** $i \in \mathcal{I}_j$, 0 otherwise. | -->
<!-- | $m_{it}$    |  =1 if resource $i \in I$ **starts a maintenance** operation in period $t \in \mathcal{T}$, 0 otherwise. | -->
<!-- | $rut_{it}$  |  **remaining usage time** (continuous) for resource $i \in I$ at the end of period $t \in \mathcal{T}$. | -->
<!-- | $ret_{it}$  |  **remaining elapsed time** (integer) for resource $i \in I$ at the end of period $t \in \mathcal{T}$. | -->
<!-- | $u_{max}$   |  maximal number (integer) of **unavailable resources** in any period. | -->
<!-- | $m_{max}$   |  maximal number (integer) of **resources in maintenance** in any period. | -->

<!-- ## Model: main constraints -->

<!-- Requirements per task: -->
<!-- ```{r out.width="250px", echo=FALSE} -->
<!-- knitr::include_graphics("./../../img/tasks_gantt.png") -->
<!-- ``` -->
<!-- \pause -->

<!-- Max maintenances: -->
<!-- ```{r out.width="150px", echo=FALSE} -->
<!-- knitr::include_graphics("./../../img/num-maintenances.png") -->
<!-- ``` -->

<!-- ## Model: main constraints -->

@@

# References
## References / Questions?

>>>>

---
title: "Maintenance planning on French military aircraft operations"
author: |
    | Franco Peschiera, Alain Haït, Olga Battaïa, Nicolas Dupin
institute: "ISAE SUPAERO"
date: "September 24, 2018"
output: 
  slidy_presentation:
    css: ./../../../css/baobab_slidy.css
    incremental: yes
    footer: "ISAE-SUPAERO, Université de Toulouse, France"
    # slide_level: 2
    # toc: true
  beamer_presentation:
    theme: "Berlin"
    toc: true
    slide_level: 2
    incremental: yes
    fig_height: 4
    # footer: "ISAE-SUPAERO, Université de Toulouse, France"
    includes:
        in_header: header.tex
bibliography: MFMP_NRP.bib
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
path_to_R_dir <- "./../../"
setwd(path_to_R_dir)
source('functions/params.R')
source('functions/import_results.R')
source('diagrams/fixed_interval.R')
exp_directory = PATHS[['experiments']] %>% paste0('201802141539/')
gantt <- print_solution(exp_directory, max_resources = 15, width='100%')
show_gantt <- knitr::opts_knit$get("rmarkdown.pandoc.to")=="slidy"
task_gantt <- tasks_gantt()
task_employees <- tasks_employees()
```

@@

if (show_gantt){
    # htmltools::HTML('<div style="font-size: 20px;width:100%">')
    # htmltools::div(style="font-size: 20px;width:100%", gantt)
    gantt
    # htmltools::HTML("</div>")
} else {
    knitr::include_graphics('../img/calendar.png' %>% paste0(path_to_R_dir, .))
}

@@

## Complexity analysis (1)

Similar to the 'Fixed interval scheduling' problem presented in @Smet2015.

@@

## Complexity analysis (2)

```{r, echo=FALSE, out.width='50%'}

if (show_gantt){
    htmltools::div(class = "row",
        htmltools::div(task_gantt, class = "col-md-6")
        ,htmltools::div(task_employees, class = "col-md-6")
        )
} else {
    knitr::include_graphics(c('../img/tasks-days.png', '../img/task-employees.png') %>% paste0(path_to_R_dir, .))
    # knitr::include_graphics('../img/task-employees.png' %>% paste0(path_to_R_dir, .))
}

@@

@@

# References

## References / Questions?
